Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2018-10-24 awipev-CO2.Rmd
add path
test_jp
ajout path

@@

```{r read and prepare discrete data, echo=FALSE, warning=FALSE, message=FALSE}
d <- read.table("../fb_data/Discrete_analyses_AT_CT/Discrete_sampling_AWIPEV.csv", header = T, dec = ".", as.is = T, sep = ";", fill = TRUE) 
d$datetime <- as.POSIXct(d$sampling_date, format="%d/%m/%Y %H:%M", tz="UTC")
d$measure_date <- dmy(d$measure_date, tz="UTC")

>>>>

#define who is the user and define path
if (Sys.getenv("LOGNAME") == "gattuso") path = "../../pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/"
if (Sys.getenv("LOGNAME") == "samir") path = "../pCloud\\ Sync/exp153_carbonates_point_B/"

@@

```{r read and prepare discrete data, echo=FALSE, warning=FALSE, message=FALSE}
d <- read.table(paste0(path, "fb_data/Discrete_analyses_AT_CT/Discrete_sampling_AWIPEV.csv"), header = T, dec = ".", as.is = T, sep = ";", fill = TRUE)
d$datetime <- as.POSIXct(d$sampling_date, format="%d/%m/%Y %H:%M", tz="UTC")
d$measure_date <- dmy(d$measure_date, tz="UTC")
